AA: the Algoritmic Autoregulation Software Development Methodology

### 2013-05-31 front-matter.tex
arrumado abstract e titulo

\title{
AA Distributed Software Development Methodology
}

@@

\begin{abstract}
We present a new self-regulating methodology for coordinating
distributed team work called Algorithmic Auto-regulation (AA), based
on recent social networking concepts and individual merit. Team
members take on an egalitarian role, and stay voluntarily logged into
so-called AA sessions for part of their time (e.g.\ 2 hours per day),
during which they create periodical logs --- short text sentences ---
they wish to share about their activity with the team. These logs are
publicly aggregated in a Website and are peer-validated, as in code
review. A video is generally recorded by the members to make their
work logs more understandable. This methodology is well-suited for
increasing the efficiency of distributed teams working on what is
called Global Software Development (GSD) through asynchronous
on-demand communication, reducing the need for central management,
unproductive meetings or time-consuming reports. The AA methodology
also legitimizes the activities of a distributed software team.  It
thus enables entities to have a solid means to fund these activities,
allowing for new and concrete business models to emerge for very
distributed software development. AA as a methodology is also at the
core of having self-replicating hacker initiatives. These claims are
discussed in a real case-study of running a distributed free software
hacker team called Lab Macambira.
\end{abstract}

>>>>

\title{
    AA: the Algoritmic Autoregulation Software Development Methodology
}

@@

\begin{abstract}
We present a new methodology for coordinating
teamwork called Algorithmic Autoregulation (AA). This methodology is based on recent social networking concepts and individual merit and exhibits convenient asynchronous, autodocumenting and autoregulating characteristics. Team
members take on an egalitarian and volutary role, by logging into
periodic ``AA sessions'' for an arbitrary duration (e.g.\ 2 hours per day).
During each session, a user creates a log composed of short text sentences
about their activity. These logs are
publicly aggregated in a Website and are peer-validated, as in code
review. A short screencast is ideally recorded at the end of each session to make
AA logs more understandable. This methodology seems to be well-suited for
increasing the efficiency of teams working on
Global Software Development (GSD). Recognized reasons for this are
the: 1) builtin asynchronous
on-demand communication, documentation and working hours comprobatives;
2) reduced need for central management,
meetings and time-consuming reports. Hence, AA
legitimizes and eases activities of a distributed software team.  It
enables groups to have new means to fund activities,
allowing for business models to emerge from
distributed software development. AA is proposed,
at it's core, as a way of having self-replicating hacker initiatives. These claims are
discussed in a real case-study of a distributed free software
hacker team called Lab Macambira.
\end{abstract}
